Efficient spherical Convolutional Neural Networks with Healpix sampling for cosmological applications

### 2018-05-07 scnn.tex
update template
a bit more

\documentclass[preprint,12pt,authoryear]{elsarticle}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=0.95\textwidth]{figures/healpix-3layers.jpg}
\caption{3 smaller sclales of the healpix sampling.}
\label{fig:healpix_sampling}
\end{figure}

@@

\begin{figure}[!ht]
\centering
% \includegraphics[width=0.45\textwidth]{figures/healpix_graph_4.pdf}
\vspace{-0.5cm}
\includegraphics[width=0.45\textwidth]{figures/half_graph_4.pdf}
\vspace{-0.5cm}
\caption{
% Left: Healpix graph for the full sphere using a nside parameter of $4$. 
Top view of a Healpix graph for half the sphere using a nside parameter of $4$.}
\label{fig:healpix_graph_4}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=0.95\textwidth]{figures/eigenvectors.pdf}
\caption{12 first graph Fourier eigenvectors.}
\label{fig:graph_harmonics}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=0.95\textwidth]{figures/gaussian_filters_sphere.pdf}
\caption{Convolution comparizon (Nside=16). 
Top: Diffusion of a unit of heat for different time $t$ using the graph. 
Bottom: spherical symmetric Gaussian smoothing for different $\sigma$ (arcmin). 
Relative difference between graph convolution and spherical smoothing: $10.4$\%, $5.7$\%, $4.8$\%, $3.8$\% }
\label{fig:gaussian_filters_comparizon}
\end{figure}

@@

\subsection{Coarsening}
The HealPix sampling present the advantage to have a natural corsening method
based on its construction. Each nside level divides each pixel into 4 subpixels.
We define the pooling process as the inverse operation grouping the 4 subpixels.
Figure~\ref{fig:pooling} illustrates the process.
\begin{figure}[!ht]
\centering
\includegraphics[width=0.95\textwidth]{figures/pooling.pdf}
\caption{Pooling illustration for 2 levels using some part of the the mollview projection. 
The final patch represent 1/12 of the sphere.}
\label{fig:pooling}
\end{figure}

@@

Leveraging the properties of the HealPix sampling, we can split each simulation
into $12*4^o$ ($o=0,1,2,\dots$) samples that span a smaller part of the sphere.
As shown in Figure~\ref{fig:subpart_sphere}, we used $o=0,1,2$ as the resulting
samples are large enough to suffer from the effet of the spherical geometry. We
decided to only report simulation results for this specific setting as spherical
cosmological data usually does not span the full sphere. However, our code
includes an example using the full sphere.

@@

\subsection{Results}

\begin{figure}[!ht]
\centering
\includegraphics[width=0.32\textwidth]{figures/result_order1.pdf}
\includegraphics[width=0.32\textwidth]{figures/result_order2.pdf}
\includegraphics[width=0.32\textwidth]{figures/result_order4.pdf}
\caption{Classification errors for the 3 different problems.}
\label{fig:results}
\end{figure}

\assign{Nathanaël, Tomek}

\begin{itemize}
	\item With the entire sphere / different PSD (The PSD features + linear SVM is equivalently good)
	\item Without the entire sphere / same PSD (1 sample: the histogram features + kernelized SVM is equivalently good)
	\item ??
\end{itemize}

Figure: Result curves

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=0.95\textwidth]{figures/gaussian_filters_spectral.pdf}
\includegraphics[width=0.95\textwidth]{figures/gaussian_filters_gnomonic.pdf}
\includegraphics[width=0.95\textwidth]{figures/gaussian_filters_section.pdf}
\caption{3 different visualizations of the convolution kernel $K_t(x)=e^{-\tau t x}$.  
Top: graph spectral domain. 
Middle: gnomonic projection.
Bottom: section plot.}
\label{fig:gaussian_filters_visualization}
\end{figure}

>>>>

% \documentclass[preprint,12pt,authoryear]{elsarticle}
\documentclass[final,twocolumn,3p,times,authoryear]{elsarticle}

@@

\begin{figure*}[!ht]
\centering
\includegraphics[width=0.7\textwidth]{figures/healpix-3layers.jpg}
\caption{3 smaller sclales of the healpix sampling.}
\label{fig:healpix_sampling}
\end{figure*}

@@

\begin{figure}[!ht]
\centering
% \includegraphics[width=0.45\textwidth]{figures/healpix_graph_4.pdf}
\vspace{-0.5cm}
\includegraphics[width=0.45\textwidth]{figures/half_graph_4.pdf}
\vspace{-0.5cm}
\caption{
Top view of a Healpix graph for half the sphere using a nside parameter of $4$.
Nodes with 7 neighboors are highlighted.
}
\label{fig:healpix_graph_4}
\end{figure}

@@

\begin{figure*}[!ht]
\centering
\includegraphics[width=0.95\textwidth]{figures/eigenvectors.pdf}
\caption{12 first graph Fourier eigenvectors.}
\label{fig:graph_harmonics}
\end{figure*}

@@

\begin{figure*}[!ht]
\centering
\includegraphics[width=0.95\textwidth]{figures/gaussian_filters_sphere.pdf}
\caption{Convolution comparizon (Nside=16). 
Top: Diffusion of a unit of heat for different time $t$ using the graph. 
Bottom: spherical symmetric Gaussian smoothing for different $\sigma$ (arcmin). 
Relative difference between graph convolution and spherical smoothing: $10.4$\%, $5.7$\%, $4.8$\%, $3.8$\% }
\label{fig:gaussian_filters_comparizon}
\end{figure*}

@@

\subsection{Coarsening}
The HealPix sampling present the advantage to have a natural corsening method
based on its construction. Each nside level divides each pixel into 4 subpixels.
We define the pooling process as the inverse operation grouping the 4 subpixels.
Figure~\ref{fig:pooling} illustrates the process.
\begin{figure}[!ht]
\centering
\includegraphics[width=0.45\textwidth]{figures/pooling.pdf}
\caption{Pooling illustration for 2 levels using some part of the the mollview projection. 
The final patch represent 1/12 of the sphere.}
\label{fig:pooling}
\end{figure}

@@

Leveraging the properties of the HealPix sampling, we can split each simulation
into $12*4^o$ ($o=0,1,2,\dots$) samples that span a smaller part of the sphere.
As shown in Figure~\ref{fig:subpart_sphere}, we used $o=0,1,2$ as the resulting
samples are large enough to suffer from the effet of the spherical geometry. We
decided to only report simulation results for this specific setting as spherical
cosmological data usually does not span the full sphere. Nevertheless, our code
includes an example using the full sphere.

@@

We would like to build a robust classifier, i.e. an automatic way to
discriminate between the two classes with the presence of noise. For all the
eperiment, we work with zero mean Gaussian noise. \todo{Tomek: could you put a
justification.} All classifiers are trained with noisy samples. To improve the
stability of the spherical CNN, we slowly increase the amount of noise added to
the training data over the iterations. Furthermore in order to avoid
overfitting, the noise is randomly produced at each iterations. We trained our
model between $5$ and $40$ epochs depending of the complexity and the size of
the problem. The testing set was simply used to assess the global performance of
the network and if the it was overfitting. 
Training took between $1$ and $10$ hours using a Nvidia 1080 TI.

We compare the spherical CNN with a handcrafted feature classifier. \cite{...}
\todo{Tomek: we need probably 1 or two other classifiers.} The features are
constructed using a normalized histogram of the values. We then train a linear
SVN classifier. We tried different kernels, but they where not leading to better
results. For a fair comparizon, we increase the amount of training data of the
SVN classifier until the testing error plateau to fix value.

\subsection{Results}
\assign{Nathanaël, Tomek}

We present in Figure~\ref{fig:results} the results for 5 different noise levels and $3$ different data sizes. The spherical neural network is always significantly better than the hand-crafted classfier.

\begin{figure}[!ht]
\centering
\includegraphics[width=0.32\textwidth]{figures/result_order1.pdf}
\includegraphics[width=0.32\textwidth]{figures/result_order2.pdf}
\includegraphics[width=0.32\textwidth]{figures/result_order4.pdf}
\caption{Classification errors for the 3 different problems. \nati{TODO: order is not correct} }
\label{fig:results}
\end{figure}

@@

\begin{figure*}[!ht]
\centering
\includegraphics[width=0.95\textwidth]{figures/gaussian_filters_spectral.pdf}
\includegraphics[width=0.95\textwidth]{figures/gaussian_filters_gnomonic.pdf}
\includegraphics[width=0.95\textwidth]{figures/gaussian_filters_section.pdf}
\caption{3 different visualizations of the convolution kernel $K_t(x)=e^{-\tau t x}$.  
Top: graph spectral domain. 
Middle: gnomonic projection.
Bottom: section plot.}
\label{fig:gaussian_filters_visualization}
\end{figure*}
